---
title: "Private vs. Public: Does Equity Ownership Influence OB/GYN Appointment Wait Times?"
subtitle: "Primary pre-registered analysis"
author: "Muffly T, Gatson T"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
suppressMessages({
  library(readr); library(dplyr); library(tidyr); library(glmmTMB); library(gt)
})
root <- normalizePath(".", mustWork = TRUE)
source(file.path(root, "R", "pe_helpers.R"))
source(file.path(root, "R", "analysis_gates.R"))
```

# Status

**This document has not produced a result yet.** It is the real primary analysis, pre-staged
against the frozen [`SAP.lock`](SAP.lock) so that when calling finishes, running it end to end
*is* the analysis -- no script is written after the outcomes exist. Every model, gate, and table
below runs on real fielded data; nothing in this file simulates, infers, or backfills a number.

The setup chunk below fails loudly and stops the knit if the required input is not yet present,
rather than falling back to anything else. That is deliberate: `dry_run_analysis.R` is the
rehearsal-with-simulated-outcomes script; this file is not it and must never grow a simulation
fallback to make itself runnable early.

```{r require-real-data}
DB_PATH <- file.path(root, "pe_obgyn_study_database.csv")

if (!file.exists(DB_PATH)) {
  stop(
    "\n\n  primary_analysis.Rmd cannot run: ", DB_PATH, " does not exist yet.\n",
    "  This file is the real fielded database with call outcomes merged in -- it does not\n",
    "  exist until calling finishes and the REDCap export (redcap/pe_mystery_caller_call_sheet_400.csv\n",
    "  or a later export against the same instrument) is merged onto the fielded sheet.\n\n",
    "  That merge step -- REDCap raw fields (calldate1/calldate2, appdate, holdtime, transfers,\n",
    "  contacted1/contacted2) -> obtained / business_days_until_appointment / call_date /\n",
    "  appointment_date / hold_time / transfers -- does not exist in this repo yet either. It is a\n",
    "  separate, not-yet-written script, not something to improvise inside this analysis file.\n",
    "  Write it, derive obtained/business_days_until_appointment there via\n",
    "  mysterycall::mysterycall_count_business_days(), and verify its output with\n",
    "  gate_business_days_correct() before this file is run for real.\n",
    call. = FALSE
  )
}

REQUIRED_COLS <- c("NPI", "Matched Pair ID", "PE_or_Not", "State",
                   "obtained", "business_days_until_appointment",
                   "call_date", "appointment_date", "hold_time", "transfers",
                   "phone_id", "same_phone_within_pair", "SVI_geocode_via",
                   "Eligible", "Taxonomy_Is_OBGYN", "Platform_Excluded")
db <- read_csv(DB_PATH, show_col_types = FALSE)
miss <- setdiff(REQUIRED_COLS, names(db))
if (length(miss)) {
  stop("\n\n  ", DB_PATH, " is missing required column(s): ", paste(miss, collapse = ", "),
       "\n  This is not something to work around by relaxing the check -- either the merge\n",
       "  script that produces this file needs to write these columns, or the analytic\n",
       "  population columns (Eligible, Taxonomy_Is_OBGYN, Platform_Excluded; see SAP.lock's\n",
       "  2026-08-24 amendment) were not carried through.\n", call. = FALSE)
}
cat(sprintf("Loaded %s: %d rows, %d columns. Proceeding with the real primary analysis.\n",
            basename(DB_PATH), nrow(db), ncol(db)))
```

# Pre-flight gates

Every gate below is real and already exists in `R/analysis_gates.R` (or `mysterycall`); none is
written here for the first time. If any of them fail, this document must not proceed to fitting
-- fix the data or amend `SAP.lock` with a dated, reasoned entry, never edit a gate to pass.

```{r sap-and-population}
SAP     <- read_sap()
SVI_COL <- SAP[["svi_column"]]

# The analytic-population restriction is a SAP.lock amendment (2026-08-24), applied here the
# same way dry_run_analysis.R applies it: read from the plan, not re-decided in this script.
db_all      <- db                       # sensitivity_6 needs the unrestricted 200 pairs
db_eligible <- sap_restrict(db, SAP)    # primary analyses: 156 of 200 pairs

analysis_preflight(db_eligible,
                   analytic        = SVI_COL,
                   arm_col         = "PE_or_Not",
                   clustering_unit = "phone_id",
                   sap             = SAP)
```

```{r business-days-gate}
# gate_business_days_correct(): re-derives business_days_until_appointment from call_date /
# appointment_date via mysterycall::mysterycall_count_business_days() and asserts agreement.
# Catches naive calendar-day arithmetic and inclusive-start off-by-one errors in the merge
# script's output before they reach a model.
gate_business_days_correct(db_eligible)
```

# Design

```{r design}
design <- db_eligible %>%
  transmute(
    npi   = as.character(NPI),
    pair  = `Matched Pair ID`,
    State = State,
    pe    = as.integer(PE_or_Not == "PE"),
    svi   = suppressWarnings(as.numeric(.data[[SVI_COL]])),
    medicaid       = as.integer(medicaid_status == "Medicaid"),
    obtained       = as.integer(obtained),
    business_days  = as.integer(business_days_until_appointment),
    hold_time      = as.numeric(hold_time),
    transfers      = as.integer(transfers),
    phone_id                = phone_id,
    same_phone_within_pair  = same_phone_within_pair,
    SVI_geocode_via         = SVI_geocode_via
  ) %>%
  mutate(svi_z = as.numeric(scale(ifelse(is.na(svi), median(svi, na.rm = TRUE), svi)))) %>%
  mutate(cell = paste0(ifelse(pe == 1, "pe", "ctrl"), "_",
                       ifelse(medicaid == 1, "medicaid", "bcbs")))

cat(sprintf("Design: %d calls | %d clinicians | %d pairs | %d states | SVI missing: %d\n",
            nrow(design), n_distinct(design$npi), n_distinct(design$pair),
            n_distinct(design$State), sum(is.na(design$svi))))
```

# Table 1. Baseline balance

```{r table1}
t1 <- mysterycall::mysterycall_table1(
  data          = db_eligible,
  covariates    = c("State", SVI_COL, "hold_time"),
  stratify_by   = "PE_or_Not",
  include_overall = TRUE
)
t1
```

# Table 2. Appointment obtainment

```{r table2}
t2 <- design %>%
  group_by(Ownership = ifelse(pe == 1, "PE-backed", "Independent"),
          Payer = ifelse(medicaid == 1, "Medicaid", "BCBS")) %>%
  summarise(n = n(), n_obtained = sum(obtained), pct = 100 * mean(obtained), .groups = "drop") %>%
  arrange(Payer, Ownership)
t2
```

# Table 3. Wait time among clinicians who scheduled

```{r table3}
t3 <- design %>% filter(obtained == 1) %>%
  group_by(Ownership = ifelse(pe == 1, "PE-backed", "Independent"),
          Payer = ifelse(medicaid == 1, "Medicaid", "BCBS")) %>%
  summarise(n = n(), mean_days = mean(business_days), sd = sd(business_days),
           median_days = median(business_days), .groups = "drop") %>%
  arrange(Ownership, Payer)
t3

gap <- t3 %>% select(Ownership, Payer, mean_days) %>%
  tidyr::pivot_wider(names_from = Payer, values_from = mean_days) %>%
  mutate(gap_days = Medicaid - BCBS)
gap
```

# Primary and secondary models

Formulas are read from and checked against `SAP.lock` via `gate_sap()` before fitting -- the
same guard `dry_run_analysis.R` exercises, now against real data. A mismatch here means the
code is about to fit something other than what was pre-registered, and must stop before it does.

```{r formulas}
F_OB_PRIMARY   <- obtained       ~ pe + svi_z + (1 | pair)
F_WT_PRIMARY   <- business_days  ~ pe * medicaid + svi_z + (1 | pair) + (1 | npi)
F_OB_SECONDARY <- obtained       ~ pe * medicaid + svi_z + (1 | pair) + (1 | npi)

TERM_OB_PRIMARY   <- gate_sap(F_OB_PRIMARY,   "obtainment_primary",   family = "binomial", sap = SAP)
TERM_WT_PRIMARY   <- gate_sap(F_WT_PRIMARY,   "waittime_primary",     family = "nbinom2",  sap = SAP)
TERM_OB_SECONDARY <- gate_sap(F_OB_SECONDARY, "obtainment_secondary", family = "binomial", sap = SAP)
```

## Primary obtainment (Medicaid calls only)

```{r fit-obtainment-primary}
d_medicaid <- filter(design, medicaid == 1)
fit_ob_primary <- glmmTMB(F_OB_PRIMARY, family = binomial, data = d_medicaid)
summary(fit_ob_primary)
```

## Primary wait time (both payers, among clinicians who scheduled)

```{r fit-waittime-primary}
d_scheduled <- filter(design, obtained == 1)
fit_wt_primary <- glmmTMB(F_WT_PRIMARY, family = nbinom2, data = d_scheduled)
summary(fit_wt_primary)
```

`gate_overdispersion()` is written for a Poisson fit; this model is already `nbinom2` per
`SAP.lock`, so it is expected to pass without complaint here. If it does not -- if the family
name it reads is somehow Poisson rather than negative-binomial -- that is itself a defect worth
stopping on, not a warning to note and move past.

```{r overdispersion-check}
gate_overdispersion(fit_wt_primary)
```

## Secondary obtainment (both payers)

```{r fit-obtainment-secondary}
fit_ob_secondary <- glmmTMB(F_OB_SECONDARY, family = binomial, data = design)
summary(fit_ob_secondary)
```

# Table 4. Model estimates

```{r table4}
grab <- function(m, term) {
  co <- summary(m)$coefficients$cond
  if (!term %in% rownames(co)) return(c(est = NA, lo = NA, hi = NA, p = NA))
  b <- co[term, "Estimate"]; se <- co[term, "Std. Error"]
  c(est = exp(b), lo = exp(b - 1.96 * se), hi = exp(b + 1.96 * se), p = co[term, "Pr(>|z|)"])
}

stopifnot(identical(TERM_WT_PRIMARY, "pe:medicaid"), identical(TERM_OB_SECONDARY, "pe:medicaid"))

t4 <- bind_rows(
  tibble(Model = "Primary obtainment (Medicaid only)", Term = "PE",
        !!!setNames(as.list(grab(fit_ob_primary, "pe")), c("est", "lo", "hi", "p"))),
  tibble(Model = "Primary wait time", Term = "PE x Medicaid",
        !!!setNames(as.list(grab(fit_wt_primary, TERM_WT_PRIMARY)), c("est", "lo", "hi", "p"))),
  tibble(Model = "Secondary obtainment", Term = "PE x Medicaid",
        !!!setNames(as.list(grab(fit_ob_secondary, TERM_OB_SECONDARY)), c("est", "lo", "hi", "p")))
) %>% mutate(CI = sprintf("%.2f-%.2f", lo, hi))
t4
```

# Supplemental Table 1. Variance components

```{r variance-components}
vc <- function(m, lbl) {
  v <- glmmTMB::VarCorr(m)$cond
  cat(sprintf("  %-30s pair var = %.4f%s\n", lbl, as.numeric(v$pair),
              if ("npi" %in% names(v)) sprintf(" | clinician var = %.4f", as.numeric(v$npi)) else ""))
}
vc(fit_ob_primary,   "Primary obtainment")
vc(fit_wt_primary,   "Primary wait time")
vc(fit_ob_secondary, "Secondary obtainment")
```

# Pre-specified sensitivities

All seven are declared in `SAP.lock`. None is optional, and none is run only if the primary
result needs support -- report all seven regardless of what the primary analysis shows.

```{r sensitivities}
sens_results <- list()

refit_wt <- function(d, formula = F_WT_PRIMARY, label) {
  m <- tryCatch(glmmTMB(formula, family = nbinom2, data = filter(d, obtained == 1)),
               error = function(e) NULL)
  sens_results[[label]] <<- if (is.null(m)) NA else grab(m, "pe:medicaid")
  m
}

# sensitivity_1: exclude pairs where same_phone_within_pair is TRUE
d_s1 <- design %>% group_by(pair) %>%
  filter(!any(same_phone_within_pair, na.rm = TRUE)) %>% ungroup()
refit_wt(d_s1, label = "sensitivity_1: exclude same-phone pairs")

# sensitivity_2: cluster on phone_id rather than npi
F_WT_S2 <- business_days ~ pe * medicaid + svi_z + (1 | pair) + (1 | phone_id)
refit_wt(design, formula = F_WT_S2, label = "sensitivity_2: cluster on phone_id")

# sensitivity_3: restrict to pairs where both members have address-level SVI linkage
# (SVI_geocode_via distinguishes true tract-level geocoding from the ZCTA area-weighted
# fallback build_svi_covariate.R uses when an address can't be placed -- see that script's
# fallback block for the exact string.)
d_s3 <- design %>% group_by(pair) %>%
  filter(all(!is.na(SVI_geocode_via) &
            SVI_geocode_via != "ZCTA area-weighted (address unplaceable)")) %>% ungroup()
refit_wt(d_s3, label = "sensitivity_3: address-level SVI only")

# sensitivity_4: refit without svi_z
F_WT_S4 <- business_days ~ pe * medicaid + (1 | pair) + (1 | npi)
refit_wt(design, formula = F_WT_S4, label = "sensitivity_4: without svi_z")

# sensitivity_5: complete-case on all analytic covariates
d_s5 <- design %>% filter(!is.na(svi_z), !is.na(pe), !is.na(medicaid))
refit_wt(d_s5, label = "sensitivity_5: complete-case")

# sensitivity_6: repeat on all 200 pairs, ignoring analytic_population
design_all <- db_all %>%
  transmute(npi = as.character(NPI), pair = `Matched Pair ID`,
           pe = as.integer(PE_or_Not == "PE"),
           medicaid = as.integer(medicaid_status == "Medicaid"),
           obtained = as.integer(obtained),
           business_days = as.integer(business_days_until_appointment),
           svi = suppressWarnings(as.numeric(.data[[SVI_COL]]))) %>%
  mutate(svi_z = as.numeric(scale(ifelse(is.na(svi), median(svi, na.rm = TRUE), svi))))
refit_wt(design_all, label = "sensitivity_6: all 200 pairs (unrestricted)")

# sensitivity_7: restrict to pairs where both members are OB/GYN by taxonomy, ignoring platform
d_s7_ids <- db_all %>% filter(Taxonomy_Is_OBGYN) %>% pull(`Matched Pair ID`)
d_s7_pairs <- names(which(table(d_s7_ids) == 2))
d_s7 <- design_all %>% filter(pair %in% d_s7_pairs)
refit_wt(d_s7, label = "sensitivity_7: taxonomy-only eligibility")

sens_table <- bind_rows(lapply(names(sens_results), function(nm) {
  r <- sens_results[[nm]]
  if (length(r) == 1 && is.na(r)) return(tibble(Sensitivity = nm, IRR = NA, CI = NA, p = NA))
  tibble(Sensitivity = nm, IRR = r["est"], CI = sprintf("%.2f-%.2f", r["lo"], r["hi"]), p = r["p"])
}))
sens_table
```

# Provenance

```{r provenance}
record_output_provenance(
  "primary_analysis_results.html",
  c("pe_obgyn_study_database.csv", "SAP.lock"),
  "primary_analysis.Rmd", "derived",
  path = file.path(root, "manuscript", "PROVENANCE.csv")
)
```

```{r save-results}
saveRDS(list(fit_ob_primary = fit_ob_primary, fit_wt_primary = fit_wt_primary,
            fit_ob_secondary = fit_ob_secondary, table1 = t1, table2 = t2, table3 = t3,
            table4 = t4, sensitivities = sens_table),
       file.path(root, "primary_analysis_results.rds"))
cat("Saved primary_analysis_results.rds\n")
```
