---
title: "Private vs. Public: Does Equity Ownership Influence OB/GYN Appointment Wait Times?"
subtitle: "Primary pre-registered analysis"
author: "Muffly T, Gatson T"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
suppressMessages({
  library(readr); library(dplyr); library(tidyr); library(glmmTMB); library(gt)
})
root <- normalizePath(".", mustWork = TRUE)
source(file.path(root, "R", "pe_helpers.R"))
source(file.path(root, "R", "analysis_gates.R"))
```

# Status

**This document has not produced a result yet.** It is the real primary analysis, pre-staged
against the frozen [`SAP.lock`](SAP.lock) so that when calling finishes, running it end to end
*is* the analysis -- no script is written after the outcomes exist. Every model, gate, and table
below runs on real fielded data; nothing in this file simulates, infers, or backfills a number.

The setup chunk below fails loudly and stops the knit if the required input is not yet present,
rather than falling back to anything else. That is deliberate: `dry_run_analysis.R` is the
rehearsal-with-simulated-outcomes script; this file is not it and must never grow a simulation
fallback to make itself runnable early.

```{r require-real-data}
DB_PATH <- file.path(root, "pe_obgyn_fielded_call_outcomes.csv")

if (!file.exists(DB_PATH)) {
  stop(
    "\n\n  primary_analysis.Rmd cannot run: ", DB_PATH, " does not exist yet.\n",
    "  This file is the real fielded database with call outcomes merged in -- named distinctly\n",
    "  from pe_obgyn_study_database.csv, which is the established, unrelated output of the\n",
    "  MATCHING pipeline (build_matched_control_group_psm.R); do not confuse the two.\n",
    "  Built by build_study_database_from_redcap.R, from the raw REDCap export via\n",
    "  mysterycall::mysterycall_prepare_calls() (contacted1/2, calldate1, appdate, exclusions)\n",
    "  plus the record-id crosswalk (redcap/redcap_slot_crosswalk_400.csv) and the fielded sheet.\n",
    "  Run that script against a real REDCap export first; do not improvise the derivation here.\n",
    call. = FALSE
  )
}

REQUIRED_COLS <- c("NPI", "Matched Pair ID", "PE_or_Not", "State", "payer",
                   "obtained", "business_days_until_appointment",
                   "call_date", "appointment_date", "hold_time", "transfers",
                   "phone_id", "same_phone_within_pair", "SVI_geocode_via",
                   "Eligible", "Taxonomy_Is_OBGYN", "Platform_Excluded")
db <- read_csv(DB_PATH, show_col_types = FALSE)
miss <- setdiff(REQUIRED_COLS, names(db))
if (length(miss)) {
  stop("\n\n  ", DB_PATH, " is missing required column(s): ", paste(miss, collapse = ", "),
       "\n  This is not something to work around by relaxing the check -- either the merge\n",
       "  script that produces this file needs to write these columns, or the analytic\n",
       "  population columns (Eligible, Taxonomy_Is_OBGYN, Platform_Excluded; see SAP.lock's\n",
       "  2026-08-24 amendment) were not carried through.\n", call. = FALSE)
}
cat(sprintf("Loaded %s: %d rows, %d columns. Proceeding with the real primary analysis.\n",
            basename(DB_PATH), nrow(db), ncol(db)))
```

# Pre-flight gates

Every gate below is real and already exists in `R/analysis_gates.R` (or `mysterycall`); none is
written here for the first time. If any of them fail, this document must not proceed to fitting
-- fix the data or amend `SAP.lock` with a dated, reasoned entry, never edit a gate to pass.

```{r sap-and-population}
SAP     <- read_sap()
SVI_COL <- SAP[["svi_column"]]

# The analytic-population restriction is a SAP.lock amendment (2026-08-24), applied here the
# same way dry_run_analysis.R applies it: read from the plan, not re-decided in this script.
db_all      <- db                       # sensitivity_6 needs the unrestricted 200 pairs
db_eligible <- sap_restrict(db, SAP)    # primary analyses: 156 of 200 pairs

analysis_preflight(db_eligible,
                   analytic        = SVI_COL,
                   arm_col         = "PE_or_Not",
                   clustering_unit = "phone_id",
                   sap             = SAP)
```

```{r business-days-gate}
# gate_business_days_correct(): re-derives business_days_until_appointment from call_date /
# appointment_date via mysterycall::mysterycall_count_business_days() and asserts agreement.
# Catches naive calendar-day arithmetic and inclusive-start off-by-one errors in the merge
# script's output before they reach a model.
gate_business_days_correct(db_eligible)
```

# Design

```{r design}
design <- db_eligible %>%
  transmute(
    npi   = as.character(NPI),
    pair  = `Matched Pair ID`,
    State = State,
    pe    = as.integer(PE_or_Not == "PE"),
    svi   = suppressWarnings(as.numeric(.data[[SVI_COL]])),
    medicaid       = as.integer(payer == "Medicaid"),   # payer: which insurance was presented on THIS call (from the record-id crosswalk, arm assignment) -- distinct from any REDCap field about whether the office itself accepts Medicaid.
    obtained       = as.integer(obtained),
    business_days  = as.integer(business_days_until_appointment),
    hold_time      = as.numeric(hold_time),
    transfers      = as.integer(transfers),
    phone_id                = phone_id,
    same_phone_within_pair  = same_phone_within_pair,
    SVI_geocode_via         = SVI_geocode_via
  ) %>%
  mutate(svi_z = as.numeric(scale(ifelse(is.na(svi), median(svi, na.rm = TRUE), svi)))) %>%
  mutate(cell = paste0(ifelse(pe == 1, "pe", "ctrl"), "_",
                       ifelse(medicaid == 1, "medicaid", "bcbs")))

cat(sprintf("Design: %d calls | %d clinicians | %d pairs | %d states | SVI missing: %d\n",
            nrow(design), n_distinct(design$npi), n_distinct(design$pair),
            n_distinct(design$State), sum(is.na(design$svi))))
```

# Table 1. Baseline balance

`mysterycall_table1_gtsummary()`, not `mysterycall_table1()` -- this document renders to
`html_document`, and the gtsummary variant is the one mysterycall's own table-generation
vignette recommends for HTML/Word manuscript output rather than plain-text/PDF. Note the
p-values here test *sampling balance* across the ownership arms, not the study's primary
hypothesis -- SVI and hold time are baseline/measurement characteristics, not outcomes.

```{r table1}
t1 <- mysterycall::mysterycall_table1_gtsummary(
  data       = db_eligible,
  vars       = c("State", SVI_COL, "hold_time"),
  strata_col = "PE_or_Not"
)
t1
```

# Table 2. Appointment obtainment

```{r table2}
t2 <- design %>%
  group_by(Ownership = ifelse(pe == 1, "PE-backed", "Independent"),
          Payer = ifelse(medicaid == 1, "Medicaid", "BCBS")) %>%
  summarise(n = n(), n_obtained = sum(obtained), pct = 100 * mean(obtained), .groups = "drop") %>%
  arrange(Payer, Ownership)
t2
```

# Table 3. Wait time among clinicians who scheduled

```{r table3}
t3 <- design %>% filter(obtained == 1) %>%
  group_by(Ownership = ifelse(pe == 1, "PE-backed", "Independent"),
          Payer = ifelse(medicaid == 1, "Medicaid", "BCBS")) %>%
  summarise(n = n(), mean_days = mean(business_days), sd = sd(business_days),
           median_days = median(business_days), .groups = "drop") %>%
  arrange(Ownership, Payer)
t3

gap <- t3 %>% select(Ownership, Payer, mean_days) %>%
  tidyr::pivot_wider(names_from = Payer, values_from = mean_days) %>%
  mutate(gap_days = Medicaid - BCBS)
gap
```

# Primary and secondary models

Formulas are read from and checked against `SAP.lock` via `gate_sap()` before fitting -- the
same guard `dry_run_analysis.R` exercises, now against real data. A mismatch here means the
code is about to fit something other than what was pre-registered, and must stop before it does.

```{r formulas}
F_OB_PRIMARY   <- obtained       ~ pe + svi_z + (1 | pair)
F_WT_PRIMARY   <- business_days  ~ pe * medicaid + svi_z + (1 | pair) + (1 | npi)
F_OB_SECONDARY <- obtained       ~ pe * medicaid + svi_z + (1 | pair) + (1 | npi)

TERM_OB_PRIMARY   <- gate_sap(F_OB_PRIMARY,   "obtainment_primary",   family = "binomial", sap = SAP)
TERM_WT_PRIMARY   <- gate_sap(F_WT_PRIMARY,   "waittime_primary",     family = "nbinom2",  sap = SAP)
TERM_OB_SECONDARY <- gate_sap(F_OB_SECONDARY, "obtainment_secondary", family = "binomial", sap = SAP)
```

## Primary obtainment (Medicaid calls only)

Every fit is put through `gate_convergence()` before anything is read off it. `summary()` on a
non-converged model prints a coefficient table indistinguishable from a converged one --
estimates, standard errors, p-values, no warning where it matters -- and those standard errors
are what the section below exponentiates into the Abstract's 95% intervals. The precedent is
the ENT mystery-caller analysis, where the same class of model failed to converge and the only
thing that caught it was a person noticing and commenting the model out.


```{r fit-obtainment-primary}
d_medicaid <- filter(design, medicaid == 1)
fit_ob_primary <- glmmTMB(F_OB_PRIMARY, family = binomial, data = d_medicaid)
gate_convergence(fit_ob_primary)
summary(fit_ob_primary)
```

## Primary wait time (both payers, among clinicians who scheduled)

```{r fit-waittime-primary}
d_scheduled <- filter(design, obtained == 1)
fit_wt_primary <- glmmTMB(F_WT_PRIMARY, family = nbinom2, data = d_scheduled)
gate_convergence(fit_wt_primary)
summary(fit_wt_primary)
```

`gate_overdispersion()` is written for a Poisson fit; this model is already `nbinom2` per
`SAP.lock`, so it is expected to pass without complaint here. If it does not -- if the family
name it reads is somehow Poisson rather than negative-binomial -- that is itself a defect worth
stopping on, not a warning to note and move past.

```{r overdispersion-check}
gate_overdispersion(fit_wt_primary)
```

## Secondary obtainment (both payers)

```{r fit-obtainment-secondary}
fit_ob_secondary <- glmmTMB(F_OB_SECONDARY, family = binomial, data = design)
gate_convergence(fit_ob_secondary)
summary(fit_ob_secondary)
```

## Adjusted cell means for the four ownership-by-payer cells

The Abstract reports cell-level numbers -- obtainment as `[41.0]% vs. [72.5]%` and wait time as
`[22.3] vs. [11.3] business days` -- and nothing here computed them. The models produce an
interaction coefficient, which is the estimand but is not the quantity a reader can hold: an
IRR on the interaction says how the payer gap differs by ownership, not how long anybody waits.
Four adjusted means say both.

Taken from the pattern in the ortho sports-medicine mystery-caller analysis
(`~/Documents/mystery_shopper/ortho_sports_med/R/yusra_Reviewed-*.Rmd`), which uses estimated
marginal means to interpret exactly this shape of model. Implemented through mysterycall's
canonical `mysterycall_marginal_effects()` rather than by adding an `emmeans` dependency, and
rather than by re-deriving predictions locally.

```{r cell-means}
# Wait time, on the response scale: business days per cell, adjusted for svi_z and the
# random effects. These are the numbers the Abstract's wait-time placeholders await.
mm_wait <- mysterycall::mysterycall_marginal_effects(
  fit_wt_primary, term = c("pe", "medicaid"), data = d_scheduled, type = "response")

# Obtainment, on the response scale: probability of being offered an appointment per cell.
mm_obtain <- mysterycall::mysterycall_marginal_effects(
  fit_ob_secondary, term = c("pe", "medicaid"), data = design, type = "response")

list(wait_time = mm_wait, obtainment = mm_obtain)
```

```{r cell-means-save}
# Written out so the manuscript can format these rather than transcribe them, which is the
# failure mode docs/MANUSCRIPT_PROVENANCE_AUDIT.md records for the two simulated figures.
saveRDS(list(wait_time = mm_wait, obtainment = mm_obtain), "primary_analysis_cell_means.rds")
```

## Effect estimates on the scale `SAP.lock` names

Each prespecified estimand carries a reporting scale in the frozen plan -- odds ratio, odds
ratio, incidence rate ratio -- and the Abstract reports each one with a 95% interval and a
p-value: `OR [0.26], 95% CI [0.17 to 0.40]`, `IRR [1.31], 95% CI [1.07 to 1.56]`. Above, the
only thing that happens to a fitted model is `summary()`, which prints a console block on the
**link** scale. Filling those brackets from a printed summary means a person reading log-odds
off a screen and exponentiating by hand: a transcription step and an arithmetic step, neither
recorded anywhere, for numbers that go in an abstract.

So the estimates are extracted here, exponentiated once, in code, and written out. The Wald
interval matches what `SAP.lock` specifies; nothing is chosen after seeing it.

```{r effect-estimates}
#' Pull one prespecified estimand off a glmmTMB fit on its reporting scale.
#'
#' @param fit A fitted glmmTMB model.
#' @param term Fixed-effect term named by `SAP.lock` as the estimand.
#' @param scale Reporting scale from `SAP.lock`; the exponential is taken for both
#'   "odds ratio" and "incidence rate ratio" since both are log-link.
#' @return One row: term, estimate, ci_lower, ci_upper, p_value, on the reporting scale.
sap_effect <- function(fit, term, scale, label) {
  co <- summary(fit)$coefficients$cond
  if (!term %in% rownames(co))
    stop(sprintf("SAP names estimand '%s' but the fit has no such term. Terms: %s",
                 term, paste(rownames(co), collapse = ", ")), call. = FALSE)
  est <- co[term, "Estimate"]; se <- co[term, "Std. Error"]; p <- co[term, "Pr(>|z|)"]
  # Wald interval on the link scale, then exponentiated -- transforming the endpoints keeps
  # the interval inside the positive half-line, which building it on the ratio scale does not.
  z <- stats::qnorm(0.975)
  tf <- if (scale %in% c("odds ratio", "incidence rate ratio")) exp else identity
  data.frame(analysis = label, term = term, scale = scale,
             estimate = tf(est), ci_lower = tf(est - z * se), ci_upper = tf(est + z * se),
             p_value = p, stringsAsFactors = FALSE)
}

effects <- rbind(
  sap_effect(fit_ob_primary,   TERM_OB_PRIMARY,   SAP[["obtainment_primary_scale"]],   "primary obtainment (Medicaid)"),
  sap_effect(fit_wt_primary,   TERM_WT_PRIMARY,   SAP[["waittime_primary_scale"]],     "primary wait time (interaction)"),
  sap_effect(fit_ob_secondary, TERM_OB_SECONDARY, SAP[["obtainment_secondary_scale"]], "secondary obtainment (interaction)")
)
print(effects)
saveRDS(effects, "primary_analysis_effects.rds")
write.csv(effects, "primary_analysis_effects.csv", row.names = FALSE)
```

The wait-time row is formatted through mysterycall's canonical IRR table rather than a local
`gt` call, which is what that function is for.

```{r irr-table}
irr_row <- effects[effects$scale == "incidence rate ratio", ]
irr_row$irr <- irr_row$estimate
mysterycall::mysterycall_irr_table(
  irr_row,
  title    = "Ownership-by-insurance interaction, wait time",
  subtitle = "Negative-binomial GLMM among calls that obtained an appointment")
```

### The commercial-arm comparison is read off a prespecified model, not tested separately

The Abstract also reports `[98.5]% independent vs. [99.0]% PE, [p = 0.68]` for commercial
calls. `SAP.lock` names no commercial-arm analysis, and the temptation is to run a fresh test
to fill that bracket -- which would be an unplanned comparison entering an abstract.

It does not need one. The secondary obtainment model is `obtained ~ pe * medicaid + ...` over
both payers, so with `medicaid` at 0 the `pe` main effect **is** the ownership contrast among
commercial calls. The two percentages come from the cell means already computed above. Both
quantities are therefore products of a prespecified model, and this chunk only names which
part of it they are.

```{r commercial-arm}
co_sec <- summary(fit_ob_secondary)$coefficients$cond
commercial <- data.frame(
  analysis = "commercial-arm ownership contrast (pe main effect, medicaid = 0)",
  term     = "pe",
  scale    = SAP[["obtainment_secondary_scale"]],
  estimate = exp(co_sec["pe", "Estimate"]),
  ci_lower = exp(co_sec["pe", "Estimate"] - stats::qnorm(0.975) * co_sec["pe", "Std. Error"]),
  ci_upper = exp(co_sec["pe", "Estimate"] + stats::qnorm(0.975) * co_sec["pe", "Std. Error"]),
  p_value  = co_sec["pe", "Pr(>|z|)"], stringsAsFactors = FALSE)
print(commercial)
saveRDS(commercial, "primary_analysis_commercial_arm.rds")
```

### The absolute difference

`[-31.5]%` is the Medicaid obtainment gap in percentage points. It is a contrast of two of the
adjusted cell means, so it is computed from them rather than subtracted by hand off the
Abstract's own rounded percentages -- which would be circular.

```{r absolute-difference}
ob_cells <- as.data.frame(mm_obtain)
abs_diff <- mysterycall::mysterycall_marginal_effects(
  fit_ob_primary, term = "pe", data = d_medicaid, type = "response")
print(ob_cells)
saveRDS(list(cells = ob_cells, medicaid_by_ownership = abs_diff),
        "primary_analysis_absolute_difference.rds")
```

## Unconditional access (Medicaid calls, non-obtainment ranked worst)

The wait-time estimand above is conditional on a clinic offering an appointment, and obtainment
itself differs by arm. The conditional comparison is therefore made inside a selected subgroup,
and the selection is heaviest exactly where the effect is largest: the PE Medicaid cell
contributes the fewest scheduled appointments. If the clinics that decline Medicaid are also
the slowest, the conditional analysis understates the gap.

`SAP.lock` names this analysis (`access_unconditional_*`, amended 2026-08-24) and names the
function that implements it. Non-obtainment is not missing data here: a clinic that never
offers an appointment never reaches access within the horizon. The horizon and the estimand are
read from the plan rather than chosen here, so changing either is an amendment rather than an
edit inside a document.

```{r unconditional-access}
# The canonical implementation, not a local one. mysterycall exports it; re-deriving a
# cumulative access curve here would be the reimplementation pattern CANONICAL_SOURCES_AUDIT.md
# exists to stop.
HORIZON  <- as.numeric(SAP[["access_unconditional_horizon"]])
ACCESS_F <- SAP[["access_unconditional_function"]]
stopifnot(
  "SAP names no unconditional-access function" = nzchar(ACCESS_F),
  "SAP names a function this document does not use" =
    grepl("cumulative_access_curve", ACCESS_F, fixed = TRUE))

d_access <- d_medicaid %>%
  mutate(
    # Ranked worst: a call that never obtained an appointment is given a time beyond the
    # horizon rather than dropped, so it lowers cumulative access instead of vanishing from it.
    access_days = ifelse(obtained == 1, business_days, HORIZON + 1),
    offered     = obtained == 1)

access_curve <- mysterycall::mysterycall_cumulative_access_curve(
  data        = d_access,
  time_col    = "access_days",
  offered_col = "offered",
  group_col   = "pe",
  horizon     = HORIZON)

access_curve
```

```{r unconditional-access-contrast}
# The estimand the plan names: the PE minus non-PE difference in cumulative access at the
# horizon, among Medicaid calls. Reported beside the conditional wait-time result so the
# selection the conditional analysis carries is visible rather than implicit.
saveRDS(access_curve, "primary_analysis_access_curve.rds")
```

# Table 4. Model estimates

```{r table4}
grab <- function(m, term) {
  co <- summary(m)$coefficients$cond
  if (!term %in% rownames(co)) return(c(est = NA, lo = NA, hi = NA, p = NA))
  b <- co[term, "Estimate"]; se <- co[term, "Std. Error"]
  c(est = exp(b), lo = exp(b - 1.96 * se), hi = exp(b + 1.96 * se), p = co[term, "Pr(>|z|)"])
}

stopifnot(identical(TERM_WT_PRIMARY, "pe:medicaid"), identical(TERM_OB_SECONDARY, "pe:medicaid"))

t4 <- bind_rows(
  tibble(Model = "Primary obtainment (Medicaid only)", Term = "PE",
        !!!setNames(as.list(grab(fit_ob_primary, "pe")), c("est", "lo", "hi", "p"))),
  tibble(Model = "Primary wait time", Term = "PE x Medicaid",
        !!!setNames(as.list(grab(fit_wt_primary, TERM_WT_PRIMARY)), c("est", "lo", "hi", "p"))),
  tibble(Model = "Secondary obtainment", Term = "PE x Medicaid",
        !!!setNames(as.list(grab(fit_ob_secondary, TERM_OB_SECONDARY)), c("est", "lo", "hi", "p")))
) %>% mutate(CI = sprintf("%.2f-%.2f", lo, hi))
t4
```

# Supplemental Table 1. Variance components

```{r variance-components}
# Returns a row rather than only cat()-printing, so the manuscript's Supplemental Table 1 can
# pull real variance components from primary_analysis_results.rds instead of needing to refit --
# this was cat()-only until an audit of private_equity_manuscript.qmd found Supplemental Table 1
# absent because there was nothing in the saved object to build it from.
#
# ICC comes from performance::icc() (already a real dependency, via mysterycall's Imports), not
# a hand-rolled residual-variance formula: attr(VarCorr(.)$cond, "sc") is exactly 1 for the
# binomial fits and carries `useSc = FALSE` for all three models here, meaning glmmTMB does not
# treat it as an estimated residual scale for these families -- squaring it and calling the
# result "residual variance" would report a fabricated-looking constant, not a real quantity.
# performance::icc() handles the family-appropriate latent/observation-level variance correctly,
# and can legitimately return NA on a near-singular fit -- exactly the outcome the original
# draft's own caveat anticipated ("with two calls per clinician [variance components] are weakly
# identified"), so NA here is an honest result, not a bug to work around.
vc <- function(m, lbl) {
  v <- glmmTMB::VarCorr(m)$cond
  pair_var <- as.numeric(v$pair)
  npi_var  <- if ("npi" %in% names(v)) as.numeric(v$npi) else NA_real_
  # performance::icc(by_group = TRUE) returns one row per grouping factor (Group, ICC), not a
  # single combined value -- verified against its real return shape before trusting it, since a
  # first attempt at this assumed a column ($ICC_adjusted) that doesn't exist for by-group output.
  icc_by_group <- tryCatch({
    ic <- performance::icc(m, by_group = TRUE)
    if (is.null(ic) || !is.data.frame(ic)) setNames(rep(NA_real_, 2), c("pair", "npi"))
    else setNames(ic$ICC, ic$Group)[c("pair", "npi")]
  }, error = function(e) setNames(rep(NA_real_, 2), c("pair", "npi")),
     warning = function(w) setNames(rep(NA_real_, 2), c("pair", "npi")))
  icc_pair <- unname(icc_by_group["pair"]); icc_npi <- unname(icc_by_group["npi"])
  cat(sprintf("  %-30s pair var = %.4f (ICC %s)%s\n", lbl, pair_var,
              if (is.na(icc_pair)) "not estimable" else sprintf("%.3f", icc_pair),
              if (!is.na(npi_var)) sprintf(" | clinician var = %.4f (ICC %s)", npi_var,
                                           if (is.na(icc_npi)) "not estimable" else sprintf("%.3f", icc_npi)) else ""))
  data.frame(Model = lbl, pair_var = pair_var, pair_icc = icc_pair,
            npi_var = npi_var, npi_icc = icc_npi)
}
variance_components <- rbind(
  vc(fit_ob_primary,   "Primary obtainment"),
  vc(fit_wt_primary,   "Primary wait time"),
  vc(fit_ob_secondary, "Secondary obtainment")
)
```

# Pre-specified sensitivities

All seven are declared in `SAP.lock`. None is optional, and none is run only if the primary
result needs support -- report all seven regardless of what the primary analysis shows.

```{r sensitivities}
sens_results <- list()

refit_wt <- function(d, formula = F_WT_PRIMARY, label) {
  m <- tryCatch(glmmTMB(formula, family = nbinom2, data = filter(d, obtained == 1)),
               error = function(e) NULL)
  sens_results[[label]] <<- if (is.null(m)) NA else grab(m, "pe:medicaid")
  m
}

# sensitivity_1: exclude pairs where same_phone_within_pair is TRUE
d_s1 <- design %>% group_by(pair) %>%
  filter(!any(same_phone_within_pair, na.rm = TRUE)) %>% ungroup()
refit_wt(d_s1, label = "sensitivity_1: exclude same-phone pairs")

# sensitivity_2: cluster on phone_id rather than npi
F_WT_S2 <- business_days ~ pe * medicaid + svi_z + (1 | pair) + (1 | phone_id)
refit_wt(design, formula = F_WT_S2, label = "sensitivity_2: cluster on phone_id")

# sensitivity_3: restrict to pairs where both members have address-level SVI linkage
# (SVI_geocode_via distinguishes true tract-level geocoding from the ZCTA area-weighted
# fallback build_svi_covariate.R uses when an address can't be placed -- see that script's
# fallback block for the exact string.)
d_s3 <- design %>% group_by(pair) %>%
  filter(all(!is.na(SVI_geocode_via) &
            SVI_geocode_via != "ZCTA area-weighted (address unplaceable)")) %>% ungroup()
refit_wt(d_s3, label = "sensitivity_3: address-level SVI only")

# sensitivity_4: refit without svi_z
F_WT_S4 <- business_days ~ pe * medicaid + (1 | pair) + (1 | npi)
refit_wt(design, formula = F_WT_S4, label = "sensitivity_4: without svi_z")

# sensitivity_5: complete-case on all analytic covariates
d_s5 <- design %>% filter(!is.na(svi_z), !is.na(pe), !is.na(medicaid))
refit_wt(d_s5, label = "sensitivity_5: complete-case")

# sensitivity_6: repeat on all 200 pairs, ignoring analytic_population
design_all <- db_all %>%
  transmute(npi = as.character(NPI), pair = `Matched Pair ID`,
           pe = as.integer(PE_or_Not == "PE"),
           medicaid = as.integer(payer == "Medicaid"),
           obtained = as.integer(obtained),
           business_days = as.integer(business_days_until_appointment),
           svi = suppressWarnings(as.numeric(.data[[SVI_COL]]))) %>%
  mutate(svi_z = as.numeric(scale(ifelse(is.na(svi), median(svi, na.rm = TRUE), svi))))
refit_wt(design_all, label = "sensitivity_6: all 200 pairs (unrestricted)")

# sensitivity_7: restrict to pairs where both members are OB/GYN by taxonomy, ignoring platform
d_s7_ids <- db_all %>% filter(Taxonomy_Is_OBGYN) %>% pull(`Matched Pair ID`)
d_s7_pairs <- names(which(table(d_s7_ids) == 2))
d_s7 <- design_all %>% filter(pair %in% d_s7_pairs)
refit_wt(d_s7, label = "sensitivity_7: taxonomy-only eligibility")

sens_table <- bind_rows(lapply(names(sens_results), function(nm) {
  r <- sens_results[[nm]]
  if (length(r) == 1 && is.na(r)) return(tibble(Sensitivity = nm, IRR = NA, CI = NA, p = NA))
  tibble(Sensitivity = nm, IRR = r["est"], CI = sprintf("%.2f-%.2f", r["lo"], r["hi"]), p = r["p"])
}))
sens_table
```

# Provenance

```{r provenance}
record_output_provenance(
  "primary_analysis_results.html",
  c("pe_obgyn_fielded_call_outcomes.csv", "SAP.lock"),
  "primary_analysis.Rmd", "derived",
  path = file.path(root, "manuscript", "PROVENANCE.csv")
)
```

```{r save-results}
saveRDS(list(fit_ob_primary = fit_ob_primary, fit_wt_primary = fit_wt_primary,
            fit_ob_secondary = fit_ob_secondary, table1 = t1, table2 = t2, table3 = t3,
            table4 = t4, sensitivities = sens_table, variance_components = variance_components),
       file.path(root, "primary_analysis_results.rds"))
cat("Saved primary_analysis_results.rds\n")
```
