---
title: "Access to Generalist Obstetrics and Gynecology Care at Private Equity-Backed vs. Independent Practices: A Mystery Caller Audit Study"
author:
  - name: Tyler Muffly
    degrees: MD
    email: tyler.muffly@dhha.org
    corresponding: true
    affiliations:
      - ref: dh
  - name: "Lizeth [SURNAME NEEDED]"
    degrees: "[CREDENTIALS NEEDED]"
    affiliations:
      - ref: cu
  - name: Taylor Gatson
    degrees: MD
    affiliations:
      - ref: cu
affiliations:
  - id: dh
    name: "Department of Obstetrics and Gynecology, Denver Health and Hospital Authority"
    city: Denver
    region: Colorado
    country: USA
  - id: cu
    name: "Department of Obstetrics and Gynecology, University of Colorado School of Medicine"
    city: Aurora
    region: Colorado
    country: USA
date: today
keywords:
  - private equity
  - mystery caller
  - Medicaid
  - appointment access
  - obstetrics and gynecology
  - health disparities
params:
  abstract_limit: 250
  word_limit: 3500
bibliography: references.bib
csl: ama.csl
link-citations: true
fig-align: center
crossref:
  fig-title: Figure
  tbl-title: Table
format:
  docx:
    reference-doc: pandoc-reference.docx
    fig-cap-location: bottom
    number-sections: false
  html:
    toc: true
    toc-depth: 2
    toc-location: left
    toc-title: Contents
    number-sections: false
    embed-resources: true
    theme: cosmo
    df-print: paged
    code-tools: true
    anchor-sections: true
    smooth-scroll: true
    citations-hover: true
    link-external-newwindow: true
    lightbox: true
    fig-cap-location: bottom
  pdf:
    documentclass: article
    pdf-engine: xelatex
    geometry: margin=1in
    fontsize: 12pt
    linestretch: 2
    number-sections: false
    fig-cap-location: bottom
    fig-pos: "H"
    colorlinks: true
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage{fancyhdr}
        \pagestyle{fancy}\fancyhf{}
        \rhead{Muffly et al.}\cfoot{\thepage}
        \renewcommand{\headrulewidth}{0pt}
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk:
    dpi: 300
    out.width: "100%"
---

```{r setup, include=FALSE}
# Modeled on ~/lizeth/manuscript.qmd's Quarto conventions (that repo's own working sibling
# mystery-caller manuscript), adapted to this study's precomputed-results architecture rather
# than lizeth's live-REDCap-load-and-refit pattern: model fitting happens exactly once, in
# primary_analysis.Rmd, which this file reads from -- it does not re-fit anything, so the
# manuscript's numbers cannot drift from the gated, SAP.lock-verified analysis that produced
# them.
root <- normalizePath("..", mustWork = TRUE)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      dpi = 300, out.width = "100%")
suppressWarnings(suppressPackageStartupMessages({
  library(dplyr); library(glmmTMB); library(flextable); library(ggplot2); library(readr)
}))

## ---- formatting helpers (ported verbatim from lizeth's manuscript.qmd) -----
fp <- function(p) {
  if (is.na(p)) return("NA")
  if (p < .001) return("< .001")
  d <- if (p >= .01 && p < .10) 3 else 2
  sub("^0", "", sprintf(paste0("%.", d, "f"), p))
}
pv <- function(p) {
  if (is.na(p)) return("= NA")
  if (p < .001) return("< .001")
  paste0("= ", fp(p))
}
f2  <- function(x) sprintf("%.2f", x)
d0  <- function(x) format(round(x), big.mark = "")
pct <- function(k, n) sprintf("%.1f%%", 100 * k / n)

flextable::set_flextable_defaults(font.size = 9, padding = 3,
                                  theme_fun = flextable::theme_booktabs)
ftab <- function(df) flextable::flextable(df) |>
  flextable::bold(part = "header") |>
  flextable::autofit() |>
  flextable::set_table_properties(layout = "autofit", width = 1)

## ---- word-count utility (approximate; ported from lizeth) ------------------
.src <- tryCatch(readLines(knitr::current_input(), warn = FALSE), error = function(e) character())
wc_between <- function(start_re, end_re) {
  if (!length(.src)) return(NA_integer_)
  i0 <- grep(start_re, .src)[1]; if (is.na(i0)) return(NA_integer_)
  rest <- .src[(i0 + 1):length(.src)]
  i1   <- grep(end_re, rest)[1]
  seg  <- if (is.na(i1)) rest else rest[seq_len(i1 - 1)]
  keep <- cumsum(grepl("^```", seg)) %% 2 == 0 & !grepl("^```", seg)
  txt  <- paste(seg[keep], collapse = " ")
  txt  <- gsub("`r [^`]+`", " x ", txt)
  txt  <- gsub("\\[?@[A-Za-z0-9;@ _-]+\\]?", " ", txt)
  txt  <- gsub("<[^>]+>|[[:punct:]]", " ", txt)
  length(strsplit(trimws(txt), "\\s+")[[1]])
}
wc_abstract <- wc_between("^# Abstract", "^\\*\\*Keywords")
wc_body     <- wc_between("^# Introduction", "^# References")

## ---- load precomputed results (primary_analysis.Rmd is the only place that fits models) ----
RESULTS_PATH <- file.path(root, "primary_analysis_results.rds")
if (!file.exists(RESULTS_PATH)) {
  stop(
    "\n\n  private_equity_manuscript.qmd cannot render: ", RESULTS_PATH, " does not exist yet.\n",
    "  Render primary_analysis.Rmd first (which itself requires pe_obgyn_study_database.csv,\n",
    "  built by build_study_database_from_redcap.R from a real REDCap export). This file only\n",
    "  narrates that object -- it does not fit models or derive outcomes itself.\n",
    call. = FALSE
  )
}
R <- readRDS(RESULTS_PATH)

## ---- Table 1's matching covariates live in the matching pipeline's intermediate output, ----
## not in primary_analysis_results.rds -- pe_obgyn_final_calling_sheet_200_dedup.csv (this
## study's committed fielded sheet) carries Credentials but not Gender / Years_in_Practice /
## Open_Payments_Years, which build_matched_control_group_psm.R computes for the propensity
## model but does not currently write through to the fielded sheet. Fails closed separately
## from RESULTS_PATH so the two gaps are diagnosable independently.
MATCH_PATH <- file.path(root, "pe_obgyn_matched_calling_list.csv")
if (!file.exists(MATCH_PATH)) {
  stop(
    "\n\n  private_equity_manuscript.qmd cannot build Table 1: ", MATCH_PATH, " does not exist.\n",
    "  Table 1 (credentials, gender, years in practice, Open Payments activity) needs the\n",
    "  matching pipeline's covariates -- run build_matched_control_group_psm.R locally first.\n",
    "  These columns are not currently carried through to the committed fielded sheet.\n",
    call. = FALSE
  )
}
match_cov <- read_csv(MATCH_PATH, show_col_types = FALSE)

## ---- assemble reported statistics from the precomputed fits (no refitting) -----------------
S <- list()
S$n_total <- nrow(match_cov); S$n_pe <- sum(match_cov$PE_or_Not == "PE")
S$n_indep <- sum(match_cov$PE_or_Not == "Non-PE")

# primary obtainment (Medicaid-only, PE vs. independent)
co <- summary(R$fit_ob_primary)$coefficients$cond["pe", ]
S$ob_or <- exp(co[["Estimate"]])
S$ob_lo <- exp(co[["Estimate"]] - 1.96 * co[["Std. Error"]])
S$ob_hi <- exp(co[["Estimate"]] + 1.96 * co[["Std. Error"]])
S$ob_p  <- co[["Pr(>|z|)"]]

# primary wait time (payer x ownership interaction)
tw <- R$table4[R$table4$Model == "Primary wait time", ]
S$wt_irr <- tw$est; S$wt_lo <- tw$lo; S$wt_hi <- tw$hi; S$wt_p <- tw$p

# secondary obtainment interaction
ts <- R$table4[R$table4$Model == "Secondary obtainment", ]
S$obs_or <- ts$est; S$obs_lo <- ts$lo; S$obs_hi <- ts$hi; S$obs_p <- ts$p

# obtainment by payer x ownership cell (Table 2)
t2 <- R$table2
cell2 <- function(own, pay) t2[t2$Ownership == own & t2$Payer == pay, ]
S$bcbs_indep <- cell2("Independent", "BCBS"); S$bcbs_pe <- cell2("PE-backed", "BCBS")
S$med_indep  <- cell2("Independent", "Medicaid"); S$med_pe <- cell2("PE-backed", "Medicaid")
S$med_rd <- 100 * (S$med_pe$pct - S$med_indep$pct) / 100

# wait times by payer x ownership cell (Table 3)
t3 <- R$table3
cell3 <- function(own, pay) t3[t3$Ownership == own & t3$Payer == pay, ]
S$wt_bcbs_indep <- cell3("Independent", "BCBS"); S$wt_bcbs_pe <- cell3("PE-backed", "BCBS")
S$wt_med_indep  <- cell3("Independent", "Medicaid"); S$wt_med_pe <- cell3("PE-backed", "Medicaid")
S$gap_indep <- S$wt_med_indep$mean_days - S$wt_bcbs_indep$mean_days
S$gap_pe    <- S$wt_med_pe$mean_days    - S$wt_bcbs_pe$mean_days
```

**Corresponding author:** Tyler Muffly, MD (tyler.muffly@dhha.org).

**Disclosure statement:** The authors report no conflicts of interest. **Funding:** None.
**IRB:** `r if (exists("SAP")) "" else ""`COMIRB — protocol status stated as "exempt" in
README.md but as "approved with a waiver of consent" in the prior manuscript draft
(manuscript_cite.md); **this discrepancy is unresolved and must be reconciled against the real
COMIRB determination letter before submission, not guessed here.**
**Word count (body):** approximately `r format(round(wc_body, -2), big.mark = ",")` words.

::: {.content-visible when-format="html"}
::: {.callout-tip appearance="simple"}
**Submission checklist (working preview only, hidden from Word/PDF output).**

- Abstract: **`r wc_abstract`** words (target ≤ `r params$abstract_limit`),
  `r if (!is.na(wc_abstract) && wc_abstract <= params$abstract_limit) "✓ within limit" else "⚠ over limit"`
- Main text: **`r wc_body`** words (target ≤ `r params$word_limit`),
  `r if (!is.na(wc_body) && wc_body <= params$word_limit) "✓ within limit" else "⚠ over limit"`
- **Unresolved before submission:** second author's surname/credentials (YAML `author:`);
  COMIRB protocol number and exempt-vs.-waiver status (see IRB line above); Table 1's
  Gender/Years-in-Practice/Open-Payments columns depend on `pe_obgyn_matched_calling_list.csv`
  existing locally; backup-physician counts in the Cohort-Compliant Backup Protocol paragraph
  need re-verifying against the current 459-pair pool (an earlier draft's 101/243 were computed
  against a superseded 511-pair pool and must not be reused as-is).
:::
:::

# Abstract

**Objective:** To compare new-patient scheduling access and wait times for Medicaid versus
commercially insured patients at private equity (PE)-backed and independent obstetrics and
gynecology (OB-GYN) practices.

**Methods:** We conducted a simulated-patient (mystery caller) crossover audit of
`r S$n_total / 2` matched clinician pairs (`r S$n_total` clinicians). Trained callers requested
new-patient gynecology appointments, presenting either Medicaid or commercial preferred-provider-
organization (PPO) insurance. Co-primary outcomes were the appointment obtainment rate and the
wait time in business days. The primary obtainment comparison was PE vs. independent ownership
among Medicaid calls, estimated with a matched-pair mixed-effects logistic model; wait times were
modeled with a negative-binomial generalized linear mixed model (GLMM) testing the
ownership-by-insurance interaction.

**Results:** Commercial insurance was accepted at `r pct(S$bcbs_indep$n_obtained, S$bcbs_indep$n)`
(`r S$bcbs_indep$n_obtained`/`r S$bcbs_indep$n`) of independent-practice calls vs.
`r pct(S$bcbs_pe$n_obtained, S$bcbs_pe$n)` (`r S$bcbs_pe$n_obtained`/`r S$bcbs_pe$n`) of PE-backed
calls. Medicaid acceptance was `r pct(S$med_indep$n_obtained, S$med_indep$n)`
(`r S$med_indep$n_obtained`/`r S$med_indep$n`) at independent clinics vs.
`r pct(S$med_pe$n_obtained, S$med_pe$n)` (`r S$med_pe$n_obtained`/`r S$med_pe$n`) at PE-backed
clinics (OR `r f2(S$ob_or)`, 95% CI `r f2(S$ob_lo)` to `r f2(S$ob_hi)`; *P* `r pv(S$ob_p)`). Among
clinics that scheduled an appointment, the insurance wait-time gap was
`r d0(S$gap_indep)` days at independent practices vs. `r d0(S$gap_pe)` days at PE-backed practices
(interaction IRR `r f2(S$wt_irr)`, 95% CI `r f2(S$wt_lo)` to `r f2(S$wt_hi)`; *P* `r pv(S$wt_p)`).

**Conclusion:** [Conclusion sentence must be written from the results above once they are real —
not carried over from the prior placeholder draft, which asserted a specific directional finding
that has not yet been observed.]

**Keywords:** private equity; mystery caller; Medicaid; appointment access; obstetrics and
gynecology; health disparities.

# Introduction

Over the past decade, corporate consolidation and financialization have reshaped the delivery of
health care in the United States. Private equity (PE) firms, which are investment partnerships
that acquire companies, restructure operations, and aim to resell them at a profit within a short
horizon (typically three to seven years), have expanded aggressively into outpatient physician
practice, acquiring hundreds of groups across specialties [@zhu2020specialties; @zhu2021ecosystem].
Obstetrics and gynecology (OB-GYN) has become a prominent target of this activity, with multiple
national women's-health "platforms" assembling large networks of acquired clinics
[@zhu2020specialties].

The returns underlying the PE model are typically pursued through administrative consolidation,
expansion of ancillary services, intensified clinician productivity, and optimization of the
"payer mix" toward higher-reimbursement commercial insurance and away from lower-reimbursement
public programs such as Medicaid. A growing evidence base links PE ownership in health care to
higher costs and mixed-to-worse quality across settings, including hospitals and physician
specialties [@borsa2023systematic; @bruch2020hospital; @kannan2023adverse]. Parallel analyses in
dermatology and ophthalmology have documented rapid PE penetration and downstream changes in
utilization and spending, raising the question of whether similar dynamics affect access in
women's health [@tan2019dermatology; @braun2024ophthalmology].

Medicaid finances approximately 41% of births in the United States and is a cornerstone of
reproductive health-care access [@kff_births]. Audit ("secret shopper") studies have repeatedly
shown that Medicaid enrollees face higher appointment-denial rates and longer waits than
commercially insured patients across specialties [@bisgaier2011auditing; @asplin2005insurance].
Yet no study has examined whether the *ownership structure* of OB-GYN practices, namely corporate
PE ownership versus traditional independent private practice, shapes these disparities. We
addressed this gap with a mystery-caller audit testing two pre-specified hypotheses: (1) PE-backed
generalist gynecology clinics decline new Medicaid patients more often than matched independent
practices; and (2) among practices that do schedule Medicaid patients, the wait-time gap between
public and commercial insurance is wider at PE-backed clinics.

# Methods

## Study Design

We conducted a simulated-patient (mystery caller) crossover audit. Trained callers contacted
generalist OB-GYN clinics posing as new patients. Each clinic was called twice: once presenting
Medicaid and once presenting commercial Blue Cross Blue Shield (BCBS) PPO coverage, at least 48
hours apart. The Colorado Multiple Institutional Review Board (COMIRB) [reviewed this protocol —
see the unresolved exempt-vs.-waiver discrepancy noted above], consistent with established
audit-study methodology [@bisgaier2011auditing].

## Cohort Identification and Matching

PE-backed OB-GYN clinics were identified using the PitchBook financial database to track
acquisitions by major women's-health platforms, and each platform's active clinician roster was
compiled from its public consumer directory. To construct a clean counterfactual, control
candidates were drawn from the CMS Doctors and Clinicians registry and matched 1-to-1 to PE
clinicians using a propensity-score matching pipeline.

Three eligibility rules were applied to the PE roster before matching. First, five platforms were
excluded because their business model cannot supply the appointment the study requests: four
fertility practices and one obstetric hospitalist group with no outpatient clinic. Second,
clinicians not observed practising within two years of the most recent year covered by the CMS
activity file were excluded as likely to have left the practice. Third, clinicians identified as
non-physicians on verification against the practice's own website were excluded.

Each PE clinician was matched 1-to-1 to a control drawn from the same state, of the same gender,
and within a 10-mile radius, requiring at least two eligible candidates inside that radius.
Propensity scores came from a logistic model of PE status on credential (MD vs. DO), gender, years
in practice, and Open Payments activity as a proxy for industry engagement; state, gender, and the
10-mile radius were enforced as hard constraints on the candidate pool. To limit within-office
clustering, exactly one clinician was randomly selected per physical office location. From a
matched pool of candidate pairs across 26 U.S. states, we fielded `r S$n_total / 2` pairs
(`r S$n_total` clinicians).

## Cohort-Compliant Backup Protocol

To protect the matched-pair structure against call-time attrition (for example, a relocated or
retired physician), backup physicians at the same office location as each primary clinician were
pre-identified before calling began [exact backup counts (PE / control) not yet re-verified
against the current 459-pair matched pool -- an earlier draft reported 101 and 243 against a
now-superseded 511-pair pool; do not reuse those figures]. Callers substituted a pre-assigned
backup only when the primary clinician was confirmed unreachable, and recorded the substitution
as a deviation in REDCap so that it remains auditable rather than silent. This is distinct from
the pair-level replacement pool described above: backups replace one clinician within an intact
pair, rather than replacing an entire pair that cannot be fielded.

## Contextual Covariates and Geographic Linkage

Neighborhood social vulnerability was measured with the Centers for Disease Control and
Prevention/Agency for Toxic Substances and Disease Registry Social Vulnerability Index
(CDC/ATSDR SVI), 2022 release, overall summary percentile ranking (`RPL_THEMES`), reconstructed
from each clinician's practice address to a 2020 census tract via the U.S. Census Bureau batch
geocoder — see `docs/CANONICAL_SOURCES_AUDIT.md` and `manuscript/appendix_data_provenance.md` for
the full provenance audit that necessitated this reconstruction.

## Call Protocol and Vignette

Callers followed a standardized script requesting a new-patient appointment for abnormal uterine
bleeding (AUB). Each caller presented either as a Medicaid enrollee or as a commercial BCBS PPO
enrollee. Insurance-presentation order was randomized, with a minimum 48-hour interval between the
two calls to a given office. Outcomes were recorded in a blinded REDCap database — record numbers
were assigned to carry no information about ownership arm (see
`docs/APPENDIX_RECORD_BLINDING.md`).

## Primary and Secondary Outcomes

The two co-primary outcomes were (1) the appointment obtainment rate, a binary indicator of
whether a scheduling date was offered, and (2) the appointment wait time, measured in business
days from the call date to the first available appointment.

## Statistical Analysis

The primary obtainment estimand is the difference in appointment obtainment between PE-backed and
independent clinicians among Medicaid calls only, estimated with a mixed-effects logistic model
containing a random intercept for the matched pair (SAP.lock: `obtained ~ pe + svi_z + (1|pair)`).

The primary wait-time estimand is the ownership-by-insurance interaction, estimated with a
negative-binomial GLMM (SAP.lock: `business_days ~ pe * medicaid + svi_z + (1|pair) + (1|npi)`).

The ownership-by-insurance interaction for obtainment is reported as a secondary analysis
(SAP.lock: `obtained ~ pe * medicaid + svi_z + (1|pair) + (1|npi)`).

Seven sensitivity analyses were specified before fielding (SAP.lock): excluding pairs sharing a
practice phone line; clustering on phone line rather than clinician; restricting to pairs with
address-level SVI linkage; refitting without the SVI covariate; complete-case analysis; repeating
the primary analyses on all 200 pairs rather than the eligibility-restricted analytic population;
and restricting eligibility to taxonomy alone. All tests were two-sided at α = 0.05.

# Results

## Baseline Cohort Demographics (Table 1)

@tbl-participants summarizes the `r S$n_total` fielded clinicians (`r S$n_pe` PE-employed,
`r S$n_indep` independent controls).

## Appointment Obtainment (Medicaid Acceptance) (Table 2)

Commercial BCBS PPO coverage was accepted in `r pct(S$bcbs_indep$n_obtained, S$bcbs_indep$n)`
(`r S$bcbs_indep$n_obtained`/`r S$bcbs_indep$n`) of independent-practice calls vs.
`r pct(S$bcbs_pe$n_obtained, S$bcbs_pe$n)` (`r S$bcbs_pe$n_obtained`/`r S$bcbs_pe$n`) of PE-backed
calls. Medicaid acceptance was `r pct(S$med_indep$n_obtained, S$med_indep$n)`
(`r S$med_indep$n_obtained`/`r S$med_indep$n`) at independent clinics vs.
`r pct(S$med_pe$n_obtained, S$med_pe$n)` (`r S$med_pe$n_obtained`/`r S$med_pe$n`) at PE-backed
clinics (primary obtainment OR `r f2(S$ob_or)`, 95% CI `r f2(S$ob_lo)` to `r f2(S$ob_hi)`;
*P* `r pv(S$ob_p)`; @tbl-results).

## Scheduling Wait Times (Table 3)

Among clinics that scheduled new-patient gynecology appointments, the insurance wait-time gap was
`r d0(S$gap_indep)` business days at independent practices vs. `r d0(S$gap_pe)` business days at
PE-backed practices (interaction IRR `r f2(S$wt_irr)`, 95% CI `r f2(S$wt_lo)` to
`r f2(S$wt_hi)`; *P* `r pv(S$wt_p)`; @tbl-results).

## Mixed-Effects Regression (Table 4)

@tbl-results presents odds ratios for obtainment and incidence rate ratios for wait time from the
SAP.lock-specified models, alongside all seven pre-specified sensitivity analyses.

# Discussion

[The Discussion, including the "dual-barrier" framing, policy implications, and limitations
carried in the prior draft (`manuscript/manuscript_cite.md`), must be rewritten from the real
results above once they exist — not carried over verbatim, since the prior draft's Discussion
asserted specific directional findings (a Medicaid access gap, a widened wait-time gap) that were
placeholders, not yet observed data. Reuse `manuscript_cite.md`'s Limitations section largely as
written; its content (single vignette, single calling week, geographic concentration, conditional
wait-time selection, clustering on shared practice lines, non-uniform SVI geocoding precision,
~69% power at the anchored effect size) describes real, already-established design properties of
this study and does not depend on the results.]

# References

::: {#refs}
:::

# Tables

```{r}
#| label: tbl-participants
#| tbl-cap: "Baseline clinician and practice characteristics of the fielded cohort."
t1 <- mysterycall::mysterycall_table1_gtsummary(
  data       = match_cov,
  vars       = c("Credentials", "Gender", "Years_in_Practice", "Open_Payments_Years"),
  strata_col = "PE_or_Not"
)
t1
```

```{r}
#| label: tbl-results
#| tbl-cap: "Appointment obtainment, wait time, and all seven pre-specified sensitivity analyses (SAP.lock), computed from the fitted models -- not re-derived here."
ci <- function(e, lo, hi) sprintf("%.2f (%.2f-%.2f)", e, lo, hi)
res <- data.frame(
  Outcome = c("Appointment obtainment (Medicaid only, primary)",
             "Appointment obtainment (ownership x payer, secondary)",
             rep("Conditional wait (primary)", 1),
             rep("Sensitivity analyses (wait-time interaction)", 7)),
  Quantity = c("PE vs. independent", "Ownership x payer interaction",
              "Ownership x payer interaction",
              sapply(R$sensitivities$Sensitivity, function(s) s)),
  Measure = c("OR", "OR", "IRR", rep("IRR", nrow(R$sensitivities))),
  `Estimate (95% CI)` = c(
    ci(S$ob_or, S$ob_lo, S$ob_hi),
    ci(S$obs_or, S$obs_lo, S$obs_hi),
    ci(S$wt_irr, S$wt_lo, S$wt_hi),
    ifelse(is.na(R$sensitivities$IRR), "not estimable",
          sprintf("%.2f (%s)", R$sensitivities$IRR, R$sensitivities$CI))),
  `P value` = c(fp(S$ob_p), fp(S$obs_p), fp(S$wt_p), sapply(R$sensitivities$p, fp)),
  check.names = FALSE, stringsAsFactors = FALSE
)
flextable::flextable(res) |>
  flextable::merge_v(j = "Outcome") |>
  flextable::valign(j = "Outcome", valign = "top") |>
  flextable::bold(part = "header") |>
  flextable::hline(i = c(2, 3), border = officer::fp_border(width = 0.5), part = "body") |>
  flextable::autofit() |>
  flextable::set_table_properties(layout = "autofit", width = 1)
```

OR, odds ratio (logistic GLMM); IRR, incidence rate ratio (negative binomial GLMM); CI,
confidence interval. The primary and secondary models are specified in `SAP.lock` and verified
against it by `gate_sap()` before fitting (`primary_analysis.Rmd`). All seven sensitivity
analyses are reported regardless of what the primary result shows.

# Figures

```{r}
#| label: fig-obtainment
#| fig-cap: "Appointment obtainment (Medicaid acceptance) rates by ownership group and payer."
ggplot(t2, aes(Payer, pct, fill = Ownership)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = sprintf("%.0f%%\n(%d/%d)", pct, n_obtained, n)),
            position = position_dodge(width = 0.7), vjust = -0.3, size = 3) +
  scale_fill_manual(values = c("Independent" = "#2c7fb8", "PE-backed" = "#d95f02")) +
  labs(x = NULL, y = "Appointment obtainment rate", fill = NULL) +
  ylim(0, 105) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

```{r}
#| label: fig-waittime
#| fig-cap: "Wait time in business days to first available appointment, by ownership group and payer, among calls that received an offer."
ggplot(t3, aes(Payer, mean_days, fill = Ownership)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_errorbar(aes(ymin = pmax(0, mean_days - sd), ymax = mean_days + sd),
                position = position_dodge(width = 0.7), width = 0.15) +
  scale_fill_manual(values = c("Independent" = "#2c7fb8", "PE-backed" = "#d95f02")) +
  labs(x = NULL, y = "Business days to appointment", fill = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

Figure 3 (STROBE flow diagram) is generated separately by `manuscript/strobe_diagram.R` via
`mysterycall_plot_inclexcl()`, not duplicated here.

# Data and Code Availability

All analysis code and the reproducible manuscript source are available in the study repository
(https://github.com/mufflyt/private_equity). All counts, ratios, and *P* values are computed from
`pe_obgyn_study_database.csv` via `primary_analysis.Rmd`, gated by `SAP.lock` and the analysis
gates in `R/analysis_gates.R`; this file narrates that precomputed object and fits no models of
its own.

# Author Contributions

<!-- CRediT roles below are a template; authors should confirm before submission. -->
T.M.: conceptualization, methodology, formal analysis, supervision, and writing – original draft.
L.[SURNAME]: investigation, data curation, and writing – review and editing.
T.G.: investigation, data curation, and writing – review and editing. All authors approved the
final manuscript.

## Computational environment

```{r}
#| label: tbl-environment
#| tbl-cap: "Software environment used to compute the reported results."
pkgver <- function(p) tryCatch(as.character(utils::packageVersion(p)), error = function(e) "not installed")
env <- data.frame(
  Component = c("R", "glmmTMB", "mysterycall", "dplyr", "Platform"),
  Version   = c(paste(R.version$major, R.version$minor, sep = "."),
                pkgver("glmmTMB"), pkgver("mysterycall"), pkgver("dplyr"), R.version$platform),
  check.names = FALSE)
ftab(env)
```
